DOM bridges and barriers: systematic review and end-user survey

### 2025-08-22 reports/lit_codes_explore.qmd
updated barriers

  #soc ba
code_freq$code_name <- replace(code_freq$code_name, code_freq$code_name == "Unintended consequences", "Indirect socioeconomic consequences")
code_freq$code_name <- replace(code_freq$code_name, code_freq$code_name == "Political permanence", "Lack of political administration permanence")
code_freq$code_name <- replace(code_freq$code_name, code_freq$code_name == "Communication & Distribution", "Poor communication and outreach")
code_freq$code_name <- replace(code_freq$code_name, code_freq$code_name == "Recipient participation", "Poor program implementation")
code_freq$code_name <- replace(code_freq$code_name, code_freq$code_name == "Cost", "Implementation costs")

@@

ggplot(data = sankey_df,
       aes(axis1 = fct_reorder(bridge_barr, -perc_codes), axis2 = fct_reorder(code_cat, -perc_codes), axis3 = fct_reorder(code_name, -perc_codes), y = perc_codes)) +
  geom_alluvium(aes(fill = code_cat, color = code_cat), size = 1.5, alpha = 0.8, width = 0.05) +
  geom_stratum(size = 1.5, color = "grey60", 
              width = c(1/12,1/12,1/3,1/3,1/3,1/3,1/3,1/3,1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18)) +
  geom_text(stat = "stratum", 
    aes(label = after_stat(stratum)),
    angle = c(90,90,0,0,0,0,0,0,0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), 
    size = c(7,7,5,5,5,5,5,5,4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4), 
    nudge_y = c(0,0,0,0,0,0,0,0,0, #poor communication and outreach
                0.5, #model abuse
                1, #lack of political permanance
                1.5, #indirect socioeconomic consequences
                1.8, #target species is a prey specialist
                2, #resource availability
                2, #climate change adding uncertainty
                2, #data transparency
                2, #need for multi-species management
                2, #distinct habitat preference
                2, #fine scale management
                1.5, #management scale system needs
                2, #management scale aligns
                0.8, #feasibility
                0,0,0,0,0,0,0,0,0,0,0,0,0,0), 
    nudge_x = c(-0.01,-0.01,0,0,0,0,0,0,0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05,   0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05), 
    hjust = c(0.5, 0.5, 0.5,0.5,0.5,0.5,0.5,0.5,0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0)) +

@@

  #calculate frequency of bridges vs. barriers being mentioned in articles -- need to add biotic and abiotic indicators cols
code_freq_new <- codes_vars2 %>%
  mutate(br_pos = as.numeric(if_any(c(33:48, 59:60), ~. == 1)), 
         ba_pos = as.numeric(if_any(49:58, ~. == 1)),
         br_dat = as.numeric(if_any(c("Management scale aligns with system needs", "Target species data availability", "Access to advanced technology and techniques", "Data transparency", "Environmental data availability", "Resource use data availability"), ~. == 1)), 
         br_eco = as.numeric(if_any(c("Expected climate change induced range shifts", "Distinct habitat preferences", "Highly mobile target species", "Life history information available for target species", "Fine scale management appropriate for target species", "Biotic indicators of target species presence", "Abiotic indicators of target species presence"), ~. == 1)), 
         br_soc = as.numeric(if_any(c("Resource availability", "Pre existing conditions", "Adoption incentives", "Feasibility", "Co management and communication"), ~. == 1)), 
         ba_dat = as.numeric(if_any(c("Gaps and inaccuracy", "Management scales do not align with system needs", "Model abuse", "Climate change adding uncertainty to target species habitat use"), ~. == 1)), 
         ba_eco = as.numeric(if_any(c("Need for multispecies management"), ~. == 1)), 
         ba_soc = as.numeric(if_any(c("Implementation costs", "Indirect socioeconomic consequences", "Lack of political administration permanence", "Poor communication and outreach", "Poor program implementation"), ~. == 1)))

@@

  #calculate frequency of bridges vs. barriers being mentioned in articles -- need to add biotic and abiotic indicators cols
soc_freq <- codes_vars2 %>%
  subset(select = c("Resource availability", "Pre existing conditions", "Adoption incentives", "Feasibility", "Co management and communication", "Indirect socioeconomic consequences", "Lack of political administration permanence", "Implementation costs", "Poor communication and outreach", "Poor program implementation")) %>%
  gather(category, pres_abs, 1:9) %>%
  mutate(br_ba = ifelse(category == "Indirect socioeconomic consequences" | category == "Lack of political administration permanence" | category == "Poor communication and outreach" | category == "Poor program implementation" | category == "Implementation costs", "Social barrier", "Social bridge")) %>%
  group_by(category, br_ba)  %>%
  summarise(n = sum(pres_abs), 
            freq = (n/118)) %>%
  mutate(percent_label = scales::percent(freq, accuracy = 2)) %>%
  group_by(category)

@@

soc_sum <- soc_freq %>%
  group_by(bridge_barr) %>%
  mutate(n_total = sum(total)) %>%
  ungroup() %>%
  group_by(code_name) %>% 
  summarise(value = total/n_total) %>%
  mutate(code_cat = ifelse(code_name == "Implementation costs" | code_name == "Indirect socioeconomic consequences" | code_name == "Lack of political administration permanence" | code_name == "Poor communication and outreach" | code_name == "Poor program implementation", "Social barrier", "Social bridge")) %>%
  mutate(percent_label = scales::percent(value, accuracy = 2))

@@

  #calculate frequency of bridges vs. barriers being mentioned in articles -- need to add biotic and abiotic indicators cols
# soc_freq <- codes_vars2 %>%
#   subset(select = c("Resource availability", "Pre existing conditions", "Adoption incentives", "Feasibility", "Co management and communication", "Indirect socioeconomic consequences", "Lack of political administration permanence", "Implementation costs", "Poor communication and outreach", "Poor program implementation")) %>%
#   gather(category, pres_abs, 1:9) %>%
#   mutate(br_ba = ifelse(category == "Indirect socioeconomic consequences" | category == "Lack of political administration permanence" | category == "Poor communication and outreach" | category == "Poor program implementation" | category == "Implementation costs", "Social barrier", "Social bridge")) %>%
#   group_by(category, br_ba)  %>%
#   summarise(n = sum(pres_abs), 
#             freq = (n/118)) %>%
#   mutate(percent_label = scales::percent(freq, accuracy = 2)) %>%
#   group_by(category)
# 
# soc_freq$category <- replace(soc_freq$category, soc_freq$category == "Co management and communication", "Co-management and communication")
# soc_freq$category <- replace(soc_freq$category, soc_freq$category == "Pre existing conditions", "Pre-existing conditions")
# soc_freq$br_ba <- factor(as.factor(soc_freq$br_ba), levels = c("Social bridge", "Social barrier"))
# 
# 
# soc_bar <- ggplot(soc_freq) +
#   geom_bar(aes(x = freq, y = reorder(category, freq), fill = br_ba), width = 0.6, stat = "identity")+
#   scale_x_continuous(position = "top", 
#                      limits = c(0,0.9),
#                      expand = c(0,0), 
#                      breaks = c(0, 0.25, 0.5, 0.75),
#                      labels = my_labs)+
#   scale_y_discrete(expand = expansion(add = c(0,0))) +
#   tidyquant::theme_tq() +
#   theme(
#     # Set background color to white
#     panel.background = element_rect(fill = "white"),
#     # Set the color and the width of the grid lines for the horizontal axis
#     panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
#     # Remove tick marks by setting their length to 0
#     axis.ticks.length = unit(0, "mm"),
#     # Remove the title for both axes
#     axis.title = element_blank(),
#     # Only left line of the vertical axis is painted in black
#     axis.line.y.left = element_line(color = "black"),
#     # But customize labels for the horizontal axis
#     axis.text.x = element_text(family = "Econ Sans Cnd", size = 16), 
#     axis.text.y = element_text(family = "Econ Sans Cnd", size = 16), 
#     legend.position = "none", 
#     strip.text = element_text(size = 16)) + 
#   geom_text(aes(x = freq, y = category, label = percent_label),
#     hjust = 0,
#     nudge_x = -0.0001,
#     colour = "black",
#     family = "Econ Sans Cnd",
#     size = 6)+
#   labs(subtitle = "Percent of sum from all articles (%)") + 
#   theme(plot.subtitle = element_text(
#       family = "Econ Sans Cnd",
#       size = 20)
#   ) + 
#   scale_fill_manual(values = c("goldenrod", "lightskyblue3"))+
#   facet_wrap(~br_ba, scales = "free", nrow = 2)
# soc_bar

@@

# soc_freq <- code_freq %>%
#   filter(code_cat == "Social bridge" | code_cat == "Social barrier")
# 
# soc_sum <- soc_freq %>%
#   group_by(bridge_barr) %>%
#   mutate(n_total = sum(total)) %>%
#   ungroup() %>%
#   group_by(code_name) %>% 
#   summarise(value = total/n_total) %>%
#   mutate(code_cat = ifelse(code_name == "Implementation costs" | code_name == "Indirect socioeconomic consequences" | code_name == "Lack of political administration permanence" | code_name == "Poor communication and outreach" | code_name == "Poor program implementation", "Social barrier", "Social bridge")) %>%
#   mutate(percent_label = scales::percent(value, accuracy = 2))
#   
# soc_sum$code_cat <- factor(as.factor(soc_sum$code_cat), levels = c("Social bridge", "Social barrier"))
# my_labs2 <- c("0", "30")
# 
# ggplot(soc_sum) +
#   geom_bar(aes(x = value, y = reorder(code_name, value), fill = code_cat), width = 0.6, stat = "identity")+
#   scale_x_continuous(position = "top", 
#                      limits = c(0,1),
#                      expand = c(0,0), 
#                      breaks = c(0,0.25, 0.5, 0.75),
#                      labels = my_labs)+
#   scale_y_discrete(expand = expansion(add = c(0,0))) +
#   tidyquant::theme_tq() +
#   theme(
#     # Set background color to white
#     panel.background = element_rect(fill = "white"),
#     # Set the color and the width of the grid lines for the horizontal axis
#     panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
#     # Remove tick marks by setting their length to 0
#     axis.ticks.length = unit(0, "mm"),
#     # Remove the title for both axes
#     axis.title = element_blank(),
#     # Only left line of the vertical axis is painted in black
#     axis.line.y.left = element_line(color = "black"),
#     # But customize labels for the horizontal axis
#     axis.text.x = element_text(family = "Econ Sans Cnd", size = 16), 
#     axis.text.y = element_text(family = "Econ Sans Cnd", size = 16), 
#     legend.position = "none", 
#     strip.text = element_text(size = 16)) + 
#   geom_text(aes(x = value, y = code_name, label = percent_label),
#     hjust = 0,
#     nudge_x = -0.0001,
#     colour = "black",
#     family = "Econ Sans Cnd",
#     size = 6)+
#   labs(subtitle = "Percent from all social bridges or barriers (%)") + 
#   theme(plot.subtitle = element_text(
#       family = "Econ Sans Cnd",
#       size = 20)
#   ) + 
#   scale_fill_manual(values = c("goldenrod", "lightskyblue3"))+
#   facet_wrap(~code_cat, scales = "free", nrow = 2)

>>>>

  #soc ba
code_freq$code_name <- replace(code_freq$code_name, code_freq$code_name == "Unintended consequences", "Indirect socioeconomic consequences")
code_freq$code_name <- replace(code_freq$code_name, code_freq$code_name == "Communication & Distribution", "Poor communication and outreach")
code_freq$code_name <- replace(code_freq$code_name, code_freq$code_name == "Recipient participation", "Poor program implementation")

@@

ggplot(data = sankey_df,
       aes(axis1 = fct_reorder(bridge_barr, -perc_codes), axis2 = fct_reorder(code_cat, -perc_codes), axis3 = fct_reorder(code_name, -perc_codes), y = perc_codes)) +
  geom_alluvium(aes(fill = code_cat, color = code_cat), size = 1.5, alpha = 0.8, width = 0.05) +
  geom_stratum(size = 1.5, color = "grey60", 
              width = c(1/12,1/12,1/3,1/3,1/3,1/3,1/3,1/3,1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18)) +
  geom_text(stat = "stratum", 
    aes(label = after_stat(stratum)),
    angle = c(90,90,0,0,0,0,0,0,0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), 
    size = c(7,7,5,5,5,5,5,5,4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4), 
    nudge_y = c(0,0,0,0,0,0,0,0,0, #poor communication and outreach
                0.5, #model abuse
                1, #Discontinuity
                1.5, #indirect socioeconomic consequences
                1.8, #target species is a prey specialist
                2, #resource availability
                2, #climate change adding uncertainty
                2, #data transparency
                2, #need for multi-species management
                2, #distinct habitat preference
                2, #fine scale management
                1.5, #management scale system needs
                2, #management scale aligns
                0.8, #feasibility
                0,0,0,0,0,0,0,0,0,0,0,0,0,0), 
    nudge_x = c(-0.01,-0.01,0,0,0,0,0,0,0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05,   0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05), 
    hjust = c(0.5, 0.5, 0.5,0.5,0.5,0.5,0.5,0.5,0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0)) +

@@

  #calculate frequency of bridges vs. barriers being mentioned in articles -- need to add biotic and abiotic indicators cols
code_freq_new <- codes_vars2 %>%
  mutate(br_pos = as.numeric(if_any(c(33:48, 59:60), ~. == 1)), 
         ba_pos = as.numeric(if_any(49:58, ~. == 1)),
         br_dat = as.numeric(if_any(c("Management scale aligns with system needs", "Target species data availability", "Access to advanced technology and techniques", "Data transparency", "Environmental data availability", "Resource use data availability"), ~. == 1)), 
         br_eco = as.numeric(if_any(c("Expected climate change induced range shifts", "Distinct habitat preferences", "Highly mobile target species", "Life history information available for target species", "Fine scale management appropriate for target species", "Biotic indicators of target species presence", "Abiotic indicators of target species presence"), ~. == 1)), 
         br_soc = as.numeric(if_any(c("Resource availability", "Pre existing conditions", "Adoption incentives", "Feasibility", "Co management and communication"), ~. == 1)), 
         ba_dat = as.numeric(if_any(c("Gaps and inaccuracy", "Management scales do not align with system needs", "Model abuse", "Climate change adding uncertainty to target species habitat use"), ~. == 1)), 
         ba_eco = as.numeric(if_any(c("Need for multispecies management"), ~. == 1)), 
         ba_soc = as.numeric(if_any(c("Cost", "Indirect socioeconomic consequences", "Discontinuity", "Poor communication and outreach", "Poor program implementation"), ~. == 1)))

@@

  #calculate frequency of bridges vs. barriers being mentioned in articles -- need to add biotic and abiotic indicators cols
soc_freq <- codes_vars2 %>%
  subset(select = c("Resource availability", "Pre existing conditions", "Adoption incentives", "Feasibility", "Co management and communication", "Indirect socioeconomic consequences", "Discontinuity", "Cost", "Poor communication and outreach", "Poor program implementation")) %>%
  gather(category, pres_abs, 1:9) %>%
  mutate(br_ba = ifelse(category == "Indirect socioeconomic consequences" | category == "Discontinuity" | category == "Poor communication and outreach" | category == "Poor program implementation" | category == "Cost", "Social barrier", "Social bridge")) %>%
  group_by(category, br_ba)  %>%
  summarise(n = sum(pres_abs), 
            freq = (n/118)) %>%
  mutate(percent_label = scales::percent(freq, accuracy = 2)) %>%
  group_by(category)

@@

soc_sum <- soc_freq %>%
  group_by(bridge_barr) %>%
  mutate(n_total = sum(total)) %>%
  ungroup() %>%
  group_by(code_name) %>% 
  summarise(value = total/n_total) %>%
  mutate(code_cat = ifelse(code_name == "Cost" | code_name == "Indirect socioeconomic consequences" | code_name == "Discontinuity" | code_name == "Poor communication and outreach" | code_name == "Poor program implementation", "Social barrier", "Social bridge")) %>%
  mutate(percent_label = scales::percent(value, accuracy = 2))

@@

  #calculate frequency of bridges vs. barriers being mentioned in articles -- need to add biotic and abiotic indicators cols
# soc_freq <- codes_vars2 %>%
#   subset(select = c("Resource availability", "Pre existing conditions", "Adoption incentives", "Feasibility", "Co management and communication", "Indirect socioeconomic consequences", "Discontinuity", "Cost", "Poor communication and outreach", "Poor program implementation")) %>%
#   gather(category, pres_abs, 1:9) %>%
#   mutate(br_ba = ifelse(category == "Indirect socioeconomic consequences" | category == "Discontinuity" | category == "Poor communication and outreach" | category == "Poor program implementation" | category == "Cost", "Social barrier", "Social bridge")) %>%
#   group_by(category, br_ba)  %>%
#   summarise(n = sum(pres_abs), 
#             freq = (n/118)) %>%
#   mutate(percent_label = scales::percent(freq, accuracy = 2)) %>%
#   group_by(category)
# 
# soc_freq$category <- replace(soc_freq$category, soc_freq$category == "Co management and communication", "Co-management and communication")
# soc_freq$category <- replace(soc_freq$category, soc_freq$category == "Pre existing conditions", "Pre-existing conditions")
# soc_freq$br_ba <- factor(as.factor(soc_freq$br_ba), levels = c("Social bridge", "Social barrier"))
# 
# 
# soc_bar <- ggplot(soc_freq) +
#   geom_bar(aes(x = freq, y = reorder(category, freq), fill = br_ba), width = 0.6, stat = "identity")+
#   scale_x_continuous(position = "top", 
#                      limits = c(0,0.9),
#                      expand = c(0,0), 
#                      breaks = c(0, 0.25, 0.5, 0.75),
#                      labels = my_labs)+
#   scale_y_discrete(expand = expansion(add = c(0,0))) +
#   tidyquant::theme_tq() +
#   theme(
#     # Set background color to white
#     panel.background = element_rect(fill = "white"),
#     # Set the color and the width of the grid lines for the horizontal axis
#     panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
#     # Remove tick marks by setting their length to 0
#     axis.ticks.length = unit(0, "mm"),
#     # Remove the title for both axes
#     axis.title = element_blank(),
#     # Only left line of the vertical axis is painted in black
#     axis.line.y.left = element_line(color = "black"),
#     # But customize labels for the horizontal axis
#     axis.text.x = element_text(family = "Econ Sans Cnd", size = 16), 
#     axis.text.y = element_text(family = "Econ Sans Cnd", size = 16), 
#     legend.position = "none", 
#     strip.text = element_text(size = 16)) + 
#   geom_text(aes(x = freq, y = category, label = percent_label),
#     hjust = 0,
#     nudge_x = -0.0001,
#     colour = "black",
#     family = "Econ Sans Cnd",
#     size = 6)+
#   labs(subtitle = "Percent of sum from all articles (%)") + 
#   theme(plot.subtitle = element_text(
#       family = "Econ Sans Cnd",
#       size = 20)
#   ) + 
#   scale_fill_manual(values = c("goldenrod", "lightskyblue3"))+
#   facet_wrap(~br_ba, scales = "free", nrow = 2)
# soc_bar

@@

# soc_freq <- code_freq %>%
#   filter(code_cat == "Social bridge" | code_cat == "Social barrier")
# 
# soc_sum <- soc_freq %>%
#   group_by(bridge_barr) %>%
#   mutate(n_total = sum(total)) %>%
#   ungroup() %>%
#   group_by(code_name) %>% 
#   summarise(value = total/n_total) %>%
#   mutate(code_cat = ifelse(code_name == "Cost" | code_name == "Indirect socioeconomic consequences" | code_name == "Discontinuity" | code_name == "Poor communication and outreach" | code_name == "Poor program implementation", "Social barrier", "Social bridge")) %>%
#   mutate(percent_label = scales::percent(value, accuracy = 2))
#   
# soc_sum$code_cat <- factor(as.factor(soc_sum$code_cat), levels = c("Social bridge", "Social barrier"))
# my_labs2 <- c("0", "30")
# 
# ggplot(soc_sum) +
#   geom_bar(aes(x = value, y = reorder(code_name, value), fill = code_cat), width = 0.6, stat = "identity")+
#   scale_x_continuous(position = "top", 
#                      limits = c(0,1),
#                      expand = c(0,0), 
#                      breaks = c(0,0.25, 0.5, 0.75),
#                      labels = my_labs)+
#   scale_y_discrete(expand = expansion(add = c(0,0))) +
#   tidyquant::theme_tq() +
#   theme(
#     # Set background color to white
#     panel.background = element_rect(fill = "white"),
#     # Set the color and the width of the grid lines for the horizontal axis
#     panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
#     # Remove tick marks by setting their length to 0
#     axis.ticks.length = unit(0, "mm"),
#     # Remove the title for both axes
#     axis.title = element_blank(),
#     # Only left line of the vertical axis is painted in black
#     axis.line.y.left = element_line(color = "black"),
#     # But customize labels for the horizontal axis
#     axis.text.x = element_text(family = "Econ Sans Cnd", size = 16), 
#     axis.text.y = element_text(family = "Econ Sans Cnd", size = 16), 
#     legend.position = "none", 
#     strip.text = element_text(size = 16)) + 
#   geom_text(aes(x = value, y = code_name, label = percent_label),
#     hjust = 0,
#     nudge_x = -0.0001,
#     colour = "black",
#     family = "Econ Sans Cnd",
#     size = 6)+
#   labs(subtitle = "Percent from all social bridges or barriers (%)") + 
#   theme(plot.subtitle = element_text(
#       family = "Econ Sans Cnd",
#       size = 20)
#   ) + 
#   scale_fill_manual(values = c("goldenrod", "lightskyblue3"))+
#   facet_wrap(~code_cat, scales = "free", nrow = 2)
